Introduction to Analysis \\ Assignment 6

### 2017-10-31 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
update

\problem{8}{Problem 25, Section 18.2, Page}

\problem{9}{Problem 26, Section 18.2, Page}

\problem{10}{Problem 27, Section 18.3, Page}
\end{document}

>>>>

\problem{8}{Problem 25, Section 18.2, Page}
\solution{Solution}{
With $\eta$ being the counting measure, suppose nonnegative $f$ on $\mathbb{N}$, and let nonnegative $f_n(x)$ be
$$
f_n(k) = \left\{
\begin{aligned}
&f(k), ~0 \le k \le n \\
&0, ~k > n
\end{aligned}
\right.
$$
then $f_n \to f$ pointwise on $\mathbb{N}$, and $\{f_n\}$ is increasing. So by Monotone Convergence Thm, 
$$
\lim_{n\to\infty}\int_{\mathbb{N}}f_n = \int_{\mathbb{N}}f.
$$
Since
$$
\int_{\mathbb{N}}f_n = \sum_{i = 1}^{n}\int_{\{i\}}f_n + \int_{\{i \ge n\}} f_n = \sum_{i=1}^{n}\int_{\{i\}}f_n = \sum_{i=1}^{n}f_n(i),
$$
we have
$$
\int_{\mathbb{N}}f = \sum_{n = 0}^{\infty}f(n) < \infty.
$$
}

\problem{9}{Problem 26, Section 18.2, Page}
\solution{Solution}{
With the definition of Dirac measure, let $g\equiv f(x_0)$, then
$$
m(\{g = f\}) = m_{\delta_{x_0}}(\{x\in X\mid f(x) = g(x)\}) = 1 = m(X).
$$
Then $f = g$, a.e. on $X$.
$$
\int_{X}f(x)d\delta_{x_0} =\int_{X}gd\delta_{x_0} = f(x_0)\int_{X}1d\delta_{x_0} = f(x_0) < \infty.
$$
}

\problem{10}{Problem 27, Section 18.3, Page}
\solution{Solution}{
a
}
\end{document}
